### 2023-01-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@db88b22e66fe7a52f34004194ca2201959f6d789 🚀

        {\bfseries Abstract:}\,Ecosystems are composed of networks of
interacting species. These interactions allow communities of species to
persist through time through both neutral and adaptive processes.
Despite their importance, a robust understanding of (and ability to
predict and forecast) interactions among species remains elusive. This
knowledge-gap is largely driven by a shortfall of data---although
species occurrence data has rapidly increased in the last decade,
species interaction data has not kept pace, largely due to the effort
required to sample interactions. This means there are many interactions
between species that occur in nature, but we do not know these
interactions occur because we have never observed them. These so-called
``false-negatives'' bias data and hinder inference about the structure
and dynamics of interaction networks. Here, we show the realized number
of false-negatives in data can be quite high, even in thoroughly sampled
systems, due to variation in abundances in a community. We provide a
null model of occurrence detection to estimate the false-negative rate
in a given dataset. We also show how to directly incorporate uncertainty
due to observation error into model-based predictions of interactions
between species. One hypothesis is interactions between ``rare'' species
are themselves rare because these species are less likely to encounter
one-another than species of higher relative abundance, and this can (in
part) explain the common pattern of nestedness in bipartite interaction
networks. However, we demonstrate that across several datasets of
spatial/temporally replicated networks, there are positive associations
between species co-occurrence and interactions, which suggests these
interactions among ``rare'' species actually exist but simply are not
observed. Finally, we assess how false negatives influence various
models of network prediction, and recommend directly accounting for
observation error in predictive models. We conclude by discussing how
the understanding of false-negatives can inform how we design monitoring
schemes for species interaction surveys.\\%

@@

>>>>

        {\bfseries Abstract:}\,Ecosystems are composed of networks of
interacting species. These interactions allow communities of species to
persist through time through both neutral and adaptive processes.
Despite their importance, a robust understanding of (and ability to
predict and forecast) interactions among species remains elusive. This
knowledge-gap is largely driven by a shortfall of data---although
species occurrence data has rapidly increased in the last decade,
species interaction data has not kept pace, largely due to the effort
required to sample interactions. This means there are many interactions
between species that occur in nature, but we do not know these
interactions occur because we have never observed them. These so-called
``false-negatives'' bias data and hinder inference about the structure
and dynamics of interaction networks. Here, we show the realized number
of false-negatives in data can be quite high, even in thoroughly sampled
systems, due to variation in abundances in a community. We provide a
null model of occurrence detection to estimate the false-negative rate
in a given dataset. We also show how to directly incorporate uncertainty
due to observation error into model-based predictions of interactions
between species. One hypothesis is interactions between ``rare'' species
are themselves rare because these species are less likely to encounter
one-another than species of higher relative abundance, and this can (in
part) explain the common pattern of nestedness in bipartite interaction
networks. However, we demonstrate that across several datasets of
spatial/temporally replicated networks, there are positive associations
between species co-occurrence and interactions, which suggests these
interactions among ``rare'' species actually exist but simply are not
observed. Finally, we assess how false negatives influence various
models of network prediction, and recommend directly accounting for
observation error in predictive models. We conclude by discussing how
the understanding of false-negatives can inform how we design monitoring
schemes for species interaction surveys.\\%
        {\bfseries Keywords:}\,species interactions, network ecology,
sampling effort, spatial ecology, null models\\%

@@

{\small{\bfseries Keywords}:\par
species interactions\\network ecology\\sampling effort\\spatial
ecology\\null models\\}
\vfill
